Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-02-26 manuscript/bef_stability/manuscript.Rmd
DiagrammeR plot ok + safer class/species metrics computation

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb, dest_dir = mypath("data", "classes"))
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin
  )
```

@@

library(ggraph)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)

library(DiagrammeR)
graph <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)

p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
```

@@

```{r sem-plot, fig.dim = c(10,10)}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
to_plot <- c(1, 6, 7)
plot_grid(
  plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
      ncol = length(to_plot), labels = LETTERS[1]),
  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3]),
  ncol = 1,
  rel_heights = c(.4, .6)
)
```

>>>>

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb, dest_dir = mypath("data", "species"))
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin
  )
```

@@

library(ggraph)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)

library(DiagrammeR)

p_format <- "png"
p_width <- 500
p_height <- 500

stab_sem_path <- mypath("manuscript", "bef_stability",
  paste0("stab_sem.", p_format))
stab_bm_path <- mypath("manuscript", "bef_stability",
  paste0("bm_sem.", p_format))

graph_stab_sem <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
render_graph(graph_stab_sem)
export_graph(graph = graph_stab_sem, file_type = p_format,
  file_name = stab_sem_path,
  height = p_height,
  width = p_width
)
#source(mypath("R", "plot_methods.R")) 
graph_bm_sem <- build_diag_from_sem(bm_sem_rich, p_val_thd = 0.05)
render_graph(graph_bm_sem)
export_graph(graph = graph_bm_sem, file_type = p_format,
  file_name = stab_bm_path,
  #file_name = "stab_sem.svg",
  height = p_height,
  width = p_width 
)

library(magick)
img_stab_sem <- mypath("manuscript", "bef_stability", "stab_sem.svg") %>%
  image_read_svg(width = 1300, height = 1000)
p_stab_sem_rich <- ggdraw() +
  draw_image(img_stab_sem)
img_bm_sem <- mypath("manuscript", "bef_stability", "bm_sem.svg") %>%
  image_read_svg(width = 1000, height = 700)
p_bm_sem_rich <- ggdraw() +
  draw_image(img_bm_sem)

@@

```{r sem-plot, fig.dim = c(10,10)}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
to_plot <- c(1, 6, 7)

plot_grid(
  plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
      ncol = length(to_plot), labels = LETTERS[1]),
  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3]),
  ncol = 1,
  rel_heights = c(.4, .6)
)
```
